---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# printMat



Provides basic functions to make it more easy to work with big matrices with long names.

## Installation

You can install the development version of printMat like so:

``` r
remotes::install_github("AlexWeinreb/printMat")
```

## head

R's defaults `print()` and `head()` attempt to print everything, filling the console. `mathead()` will trim names if necessary and only print the top-left corner of a matrix.
 
```{r example}
library(printMat)
mat <- matrix(runif(50*60), nrow = 50)
rownames(mat) <- c("qwertyuiopasdfghjkl", "123456789123456789") |> rep(25)
mathead(mat)
```

You can use it to overwrite the default `utils:::head.matrix()`:

```{r eval=FALSE}
usethis::edit_r_profile()

# and add
head.matrix <- printMat::mathead
```


# image

For big matrices, the default `image()` takes a while to render, and inverts the coordinates, `matimage()` is a small wrapper. It largely reuses the code of `imageM()` in the examples of `?image`.




